Median Maximum Pairwise Distance

### 2020-08-20 main.Rmd
null distribution

smart_harmony %>% 
  mutate(MMPD = round(MMPD, 3), max_pd = round(max_pd, 3)) %>% 
  mutate(rankn = row_number()) %>%
  rename("rankun" = "r") %>% kable()
```
## Simulation design

@@

>>>>

smart_harmony %>% 
  mutate(MMPD = round(MMPD, 3), max_pd = round(max_pd, 3)) %>% 
  mutate(rankn = row_number()) %>%
  rename("rankun" = "r") %>% kable()
```

## Null distribution

### Normalised maximum distances follow standard Gumbel distribution

### Limiting distribution of median of normalised maximum distances is normal

Let a continuous population be given with cdf F(x) (cumulative distribution function) and median $\xi$ (assumed to exist uniquely). For a sample of size $2n + 1$, let $\tilde{x}$ denote the sample median. The distribution of $\tilde{x}$,under certain conditions, to be asymptotically normal with mean $\xi$ and variance $\sigma_n^2 = \frac{1}{4} [f(\xi)]^2(2n + 1)$, where $f(x) = F'(x)$ is the pdf (probability density function).

## Simulation design

@@

 - To check if different distributions impact
(simulate with different distributions but same for all levels)

 - To check if x-levels are normalised
(simulate with different distributions)
(simulate with different x-levels)

 - To check if facet-levels are normalised
(simulate with different distributions)
(simulate with different facet-levels for fixed x-levels)
